Predicting stability of a tuneable ring laser with an iterative model

### 2020-11-15 Papers/Journal/Tuneable_Lasers.tex
Added abstract and title

\title{}
\author{B. Metherall \and C. S. Bohun}

@@

\twocolumn[
	\begin{@twocolumnfalse}
		\maketitle
		\begin{abstract}

		\end{abstract}
	\end{@twocolumnfalse}
]

>>>>

\title{Predicting stability of a tuneable ring laser with an iterative model}
\author{B. Metherall \and C. S. Bohun}

@@

\twocolumn[
	\begin{@twocolumnfalse}
		\maketitle
		\begin{abstract}
			We propose a nonlinear iterative map for tuneable ring lasers. Using the generalized nonlinear Schr\"odinger equation, expressions for the transformations undergone by the laser pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity. These transformations are then iteratively composed to give the overall effect of one round trip of the cavity. We first examine the linear version of the model which we solve analytically. Then the full nonlinear model is investigated numerically. The nonlinear model is able to exhibit wave breaking as well as modulation instability. We highlight the rich landscape and sharp divide for a particular plane of the parameter space.
		\end{abstract}
	\end{@twocolumnfalse}
]
